How do we get from object recognition\\ to object naming?

### 2018-06-28 papers/SiVL2018/objectnaming.tex

>>>>

Most research on computer vision and object recognition has somehow worked around the fact that objects can be instances of multiple, hierarchically embedded categories. 
State-of-the-art recognition models are mostly trained as classifiers on a flat of 1000 categories in ImageNet, reducing the ImageNet ontology to an inherently flat annotation scheme and treating
object labels as mutually exclusive.
